# Missing values

## Twitter Dataset 

We conducted analysis on the missing values before forming our final dataset. Of all the features, we first choose 8 features to consider. 7 out of the 8 features are introduced in the previous section, and the only feature that we left out was `geo`. The missing value graph will support our decision. Another thing worth mentioning is that all the added features will not be presented. Since they are derived from `text`, they will not contain any missing value.

Here we use the whole raw data set containing tweets from October 28th to November 3rd. There are a total of 471,996 tweets. The following is a missing value graph of our raw dataset. We modified the feature names a bit to make sure the graph is clean.

```{r}
library(tidyverse)
library(patchwork)
library(ggplot2)
```


```{r}
mvgraph <- function(df,mode="count",abbr=waiver()){
  missing_patterns <- data.frame(is.na(df)) %>%
    group_by_all() %>%
    count(name = "count", sort = TRUE) %>%
    ungroup()
  
  #Create dataframe to draw the top graph
  na_count = data.frame(colSums(is.na(df))) 
  colnames(na_count) <- "count"
  
  na_count <- na_count %>%
    rownames_to_column("variable") %>%
    mutate(variable=as.factor(variable)) 
  
  #factor level for the missing graph to follow
  mlevel = levels(fct_reorder(na_count$variable,desc(na_count$count)))
  
  #Missing count 
  if(mode == "count"){
    #Top graph
    p1 <- ggplot(na_count,aes(x=fct_reorder(variable,desc(count)),y=count)) +
      geom_bar(stat="identity",fill="skyblue",alpha=0.7) +
      xlab("") +
      ylab("# rows missing") + 
      ggtitle("Missing value patterns") +
      scale_y_continuous(n.breaks = 3) +
      theme_linedraw() +
      theme(panel.grid.major.x = element_blank()) +
      scale_x_discrete(label=abbr)
  }else if(mode == "percent"){
    na_count_p <- na_count %>% 
      mutate(percentage = count *100 / nrow(df))
    
    p1 <- ggplot(na_count_p,aes(x=fct_reorder(variable,desc(percentage)),y=percentage)) +
      geom_bar(stat="identity",fill="skyblue",alpha=0.7) +
      xlab("") +
      ylab("% rows missing") + 
      ggtitle("Missing value patterns") +
      scale_y_continuous(limits=c(0,100)) +
      theme_linedraw() +
      theme(panel.grid.major.x = element_blank()) +
      scale_x_discrete(label=abbr)}
  
  #Add index
  missing_patterns$id <- factor(1:nrow(missing_patterns))
  row_num = nrow(missing_patterns)
  col_num = ncol(df)

  mp_main <- missing_patterns %>%
    select(-count) %>%
    pivot_longer(cols=!id, names_to="variable", values_to="value")

  text_pos_x = (col_num + 1) / 2 #x-value to place the annotation

  text_pos_y <-  missing_patterns %>%
    filter_all(all_vars(.!="TRUE"))

  text_pos_y <- as.numeric(text_pos_y$id)
  text_pos_y <-  row_num + 1 - text_pos_y #y-value to place the annotation


  #Missing patterns that are not complete
  row_alpha <- missing_patterns %>%
    filter_all(any_vars(.=="TRUE")) %>%
    select(id)

  #Parameters to change alpha value in the graph
  row_alpha <- row_alpha$id #Rows that do not need to highlight
  alpha_seq <- seq(0.7,0.7,length.out=length(row_alpha)) #A sequence of alpha values

  #Missing pattern main graph
  p2 <- ggplot(mp_main,aes(x=fct_relevel(variable,mlevel),y=fct_rev(id), fill=value)) +
    geom_tile(aes(alpha=id),color="white") + 
    xlab("variable") +
    ylab("missing pattern") +
    scale_fill_manual(values = c("grey","skyblue")) +
    annotate("text",x=text_pos_x,y=text_pos_y,label="Complete case") + 
    scale_alpha_manual(values=alpha_seq,limits = row_alpha) +
    theme_classic() +
    scale_x_discrete(label=abbr) +
    theme(legend.position = "none")
  
  if(mode == "count"){
    #Missing pattern side graph
    p3 <- ggplot(missing_patterns,aes(x=fct_rev(id),y=count)) +
      geom_bar(aes(alpha=id),stat="identity",fill="skyblue") +
      xlab("") +
      ylab("row count") +
      coord_flip() + 
      scale_alpha_manual(values=alpha_seq,limits = row_alpha) +
      theme_linedraw() +
      theme(panel.grid.major.y = element_blank()) +
      theme(legend.position = "none")
  } else if(mode == "percent"){
    missing_patterns_p <- missing_patterns %>%
      mutate(percentage= 100*count / sum(count))

    p3 <- ggplot(missing_patterns_p,aes(x=fct_rev(id),y=percentage)) +
      geom_bar(aes(alpha=id),stat="identity",fill="skyblue") +
      xlab("") +
      ylab("% rows") +
      coord_flip() + 
      scale_alpha_manual(values=alpha_seq,limits = row_alpha) +
      scale_y_continuous(limits = c(0,100)) +
      theme_linedraw() +
      theme(panel.grid.major.y = element_blank())+
      theme(legend.position = "none")}
  
  p1 + plot_spacer() + p2 + p3 +
    plot_layout(widths = c(4,1),heights = c(1,4))
}
```

```{r}
EM_df <- read.csv("data/EM_df.csv")
EM_df <- EM_df %>%
  select(-X)
```

```{r}
EM_df <- EM_df[,c(1,2,3,4,6,7,8,9)]
```

```{r}
colnames(EM_df)[1] <- c("time") 
colnames(EM_df)[2] <- c("tweet_id")
colnames(EM_df)[4] <- c("geo")
colnames(EM_df)[5] <- c("user_id")
colnames(EM_df)[6] <- c("No.follower")
```

```{r}
m_geo <- sum(is.na(EM_df$geo))
m_loc <- sum(is.na(EM_df$location))
m_tweet <- sum(is.na(EM_df$full_text))
m_follower <-sum(is.na(EM_df$No.follower))
m_id <-sum(is.na(EM_df$tweet_id))

col_names <- c("geo","location","full_text","No.follower","tweet_id")
missing_v <-c(m_geo,m_loc,m_tweet,m_follower,m_id)

knitr::kable(cbind(col_names,missing_v),col.names=c("Feature","Count"),caption="Missing values")
```


```{r}
mvgraph(EM_df,mode="percent")
```

As shown in the graph, the `geo` feature has the most missing values that is close to 100%. From the documentation, `geo` is the tweet location that is tagged by the user. It indicates that Twitter users seldom specify a location for tweets. Because of the high missing percentage, we choose to remove the feature. Another largely missing data column is `location` with 5241 valid values. `location` is a self-identified location by the user, and is has the format like 'Manhattan, NY'. We think that we will be able to derive some geological pattern based on the limited data we have. The missing value in `text` is interesting. `text` can only holds up to 140 character and if a tweet exceeds the limit, `full_text` is the feature that will capture the complete contents. We see that around half of the users write short text when post tweets related to Elon Musk.

Looking at the missing patterns. More than a half of the tweets are missing `geo` and `location`, and around 46% of the tweets have additional missing value in `full_text`. The other three missing patterns are trivial. We do notice that there is a missing pattern that has missing value in every feature. We found out that there we 56 empty rows in our dataset and we removed those row in later section.